Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Updates from Overleaf

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{NSF Grant ???} }}

@@

\section{Related Work}
\textbf{Todo}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. Darwin Core developed specifically for digital museum projects is one of the most frequently used standards. Other popular standards include the Dublin Core, particularly application profiles, drawing from other namespaces such as the Ecological Metadata Language (EML) and ISO-geo [jane add]; and there is also the recent Audubon Core, designed to support the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens. These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator. In other words, their application anticipates that a curator or data entry staff person will manually enter data from the original acquisition logs, or historical labels. As a result, the metadata associated with each digital rendering seems somewhat limited, particularly to researchers seeking to apply machine learning, and leverage both the image and the metadata.
%will add cites above, depending on paper length.

@@

\subsection{Automatic Metadata Generation}
Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time, 
%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.

>>>>

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{NSF Grant ???} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., e.g., bgnn, and even mention of metadata research center. 
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. Darwin Core~\cite{biodiv_info_standards} developed specifically for digital museum projects is one of the most frequently used standards. Another approach is to create a metadata application profile by integrating properties from Dublin Core's DCMI Metadata Terms \cite{dc_terms}, the Ecological Metadata Language (EML) \cite{EML_2019} and other namespaces. There is also the recent Audubon Core supporting the discoverability, dissemination, and use of data relating to biological organisms, including digitized specimens.\cite{audub_core} These descriptive standards include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the eye of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is limited, particularly for researchers seeking to apply machine learning, and leverage both the image and the metadata for scientific research.

This limitation is magnified, when trying get a handle on the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, but metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bio-generated neural network.
%will add cites above, depending on paper length.

@@

\subsection{Automatic Metadata Generation}
Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time,  //Technical metadata capturing image lighting, camera, date of digitization and other information are automatically generated, but 
%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.
